---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## 1. Inspect the first few lines of the dataset

```{r}
  
  library(classdata)
  head(ames)
  summary(ames)
  str(ames)
  
```

### Step 1 Result

The dataset has the following variables of note: 

Style 
- Factor based variable describing the style of home (1 story, 2 story, etc.)
- 12 possible values.

Occupancy 
- Factor based variable describing how many people can live in the home. (Condominium, Single-Family, Townhouse, etc)
- 5 possible values.

Sale Date 
- Date variable saying when the home was sold. 
- Expected range between 2017-07-03 and 2022-08-31.

Sale Price 
- Numerical variable describing the price of the home when sold. 
- Expected range between 0 to 20500000. 

Year Built 
- Numerical variable with the year that the home was built. 
- Expected range between 0 and 2022. 

Acres 
- Numerical variable describing the number of acres the house has with it. 
- Expected value from 0.0 to maximum of 12.012. 

TotalLivingArea
- Numerical variable describing the square feet of the living area of the home. 
- Expected values ranging from 0 to maximum of 6007. 

Bedrooms
- Numerical value describing the number of bedrooms in the home. 
- Expected values ranging from 0.0 to 10.0.

FinishedBsmtArea 
- Numerical value describing the square feet of the finished basement.
- Expected values ranging from 10.0 to 6496.0

##2.  Is there a variable of special interest or focus?
Yes there is a variable of special interest. The sale price is a variable that we are told to look into more closely.
