---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

## 1. Inspect the first few lines of the dataset

```{r}
  
  library(classdata)
  head(ames)
  summary(ames)
  str(ames)
  
```

### Step 1 Result

The dataset has the following variables of note: 

Parcel ID

- This is a character based variable describing the ID of the transaction.
- This seems to be a 10 length character string of numbers.

Address

- This is a character based variable with the address of the place sold.
- This has a long range of strings for the address.

Style 

- Factor based variable describing the style of home (1 story, 2 story, etc.)
- 12 possible values.

Occupancy 

- Factor based variable describing how many people can live in the home. (Condominium, Single-Family, Townhouse, etc)
- 5 possible values.

Sale Date 

- Date variable saying when the home was sold. 
- Expected range between 2017-07-03 and 2022-08-31.

Sale Price 

- Numerical variable describing the price of the home when sold. 
- Expected range between 0 to 20500000. 

Year Built 

- Numerical variable with the year that the home was built. 
- Expected range between 0 and 2022. 

Acres 

- Numerical variable describing the number of acres the house has with it. 
- Expected value from 0.0 to maximum of 12.012. 

TotalLivingArea

- Numerical variable describing the square feet of the living area of the home. 
- Expected values ranging from 0 to maximum of 6007. 

Bedrooms

- Numerical value describing the number of bedrooms in the home. 
- Expected values ranging from 0.0 to 10.0.

FinishedBsmtArea 

- Numerical value describing the square feet of the finished basement.
- Expected values ranging from 10.0 to 6496.0

LotArea

- This is a numerical variable describing the total square feet of the lot.
- The expected values range from 0 to a maximum of 523228.

AC
- This is a character variable describing whether the home has AC or not.
- The expected value is either "Yes" or "No"

FirePlace
- This is a character value describing whether the home has a FirePlace or not. 
- The expected value is either "Yes" or "No"

Neighborhood
- This is a factor variable describing the neighborhood of the home being sold.
- This has 42 different categories to describe the different neighborhoods of ames.

## 2.  Is there a variable of special interest or focus?
Yes there is a variable of special interest. The sale price is a variable that we are told to look into more closely.

## 3. Start the exploration of the main variable:
```{r}
library(ggplot2)
colnames(ames)[6] = "SalePrice"

ggplot(data = ames, aes(x = SalePrice)) + geom_histogram(binwidth=900000)


```

## 4. Start Exploration of Main Vairable.

### Cassidy's Work
I am going to explore the TotalLivingArea variable.

```{r}

colnames(ames)[10] = "TotalLivingArea"

ggplot(data = ames, aes(x = TotalLivingArea)) + geom_histogram(binwidth=100)
```
As the above shows, the range of total living area is in general between 1000 square feet and 2000 square feet. However, there are outliers beyond those, with many with 0 square feet and some trailing closer to 6000. 




```{r}
ggplot(data=ames, aes(x=TotalLivingArea, y = SalePrice)) + geom_point() + ylim(0, 1.0e+06)
```

After some scaling to remove extreme outliers, it can be seen that in general, as TotalLivingArea increases the SalePrice increases. This indicates a positive correlation. However, there are some extreme oddities. Some places with 0 square feet of living area are sold for a  high price - perhaps they are places that are not meant to be lived in, and some places with high living area but sold for a very low SalePrice. To further explore this, below is a scatterplot with a more zoomed in axis.

```{r}

ggplot(data=ames, aes(x=TotalLivingArea, y = SalePrice)) + geom_point() + ylim(0, 1.0e+05)

```

This is zoomed in to show the oddities. This just further shows how many data points are still sold for 0 despite having a TotalLivingArea of >0 square feet. Perhaps this oddity cannot be fully described with just these variables.
